Reading Notes

### 2020-08-17 2pd.tex
writing about past work

\section*{Preliminary Work}
% With lan - About excitonic splitting, using DFT, DNA. 
% With Matt - What intermolecular interactions guide diphenylurea crystal formation
% With us - Perspective paper about all things

%%<how do I relate this to what I want to do??>
- contributed to development of open-source packages: mbuild, foyer, signac, fresnel
 this has helped me learn best software development practices like writing documentation, using version control, writing unit tests, employing CI, fork/pull model, etc.
using these tools will help me to me a more efficient developer.
It's also helped me to learn how to work as part of a team.
 - created MWE of coarse-graining and backmapping with smiles-- these will need further testing as we try them on different compounds but the proof of concept is there.
 - created tutorial examples to help current and future students understand scientific concepts and how to use computational tools
 %% frame gixstapose as a tool for reproducible, approachable science
 - created GIXStapose (presented at SciPy2020) an interactive diffraction/structure viewer.
This may seem unrelated but we can use diffraction to verify our opv morphologies and compare them to experiment.
GIXStapose helps to beeter connect the physical structure with the diffraction pattern.
- started development on UFF repo for foyer.
This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
%%<atom typing is a pain and doing it manually is bad cite foyer paper>

>>>>

\section*{Preliminary Work}
My prior work has involved probing the intermolecular interactions which govern dimer and crystal formation.
% With lan - About excitonic splitting, using DFT, DNA. 
Using density functional theory (DFT) to probe the excitonic splitting observed in cyanine dye dimers\cite{Fothergill2018}.

% With Matt - What intermolecular interactions guide diphenylurea crystal formation
An investigation of the supramolecular interactions which guide crystal self-assembly in diphenylurea transition metal complexes using density functional theory\cite{Millard2019a}. 
% With us - Perspective paper about all things
My contributions to our perspective paper were mostly about my experience joining the lab and trying to reproduce and existing model--something which should be very straightforward in a computational field, but which any computational scientist can attest is not simple\cite{Jankowski2019}. 
 %% frame gixstapose as a tool for reproducible, approachable science
I also presented a tool I've developed, called GIXStapose, at the Scientific Python conference (SciPy2020). %%cite scipy and gixstapose
GIXStapose is an interactive structure viewer alongside its simulated diffraction pattern.
This work had two goals: helping users to see the connections between a structure and it's diffraction pattern and making reproducible figure generation easier.
The first goal is achieved through a graphical user interface (GUI) which allows users to interact with the structure using the mouse and the diffraction pattern is updated automatically.
The second goal is accomplished by allowing all steps of the figure generation process (e.g., positioning the camera, setting the colors and lighting, etc) to be scripted and never \testit{requiring} use of the GUI.

These prior works, although not directly related to OPVS or coarse grain models, have helped me think about how atomic interactions can shape a structure, the struggles that face a new computational scientist, and how I can help.

%%<how do I relate this to what I want to do??>
I have contributed to development of open-source packages: mbuild, foyer, signac, fresnel
These contributions have given me ample opportunity to excercise best software development practices like writing good documentation, using version control, writing unit tests, employing CI, using a fork \& pull workflow, etc.
This experience will help me to be more efficient in my future work.
I've also gained valuable experience as working as part of a team.
As I plan to integrate my future work with existing projects, good collaborate skills will be necessary.

%% experience teaching and creating material for people to learn
I have completed Software Carpentry training which has taught me how to break down complex ideas and give learners a chance to use their knowledge.
With these principles in mind, I have created tutorial examples to help current and future students understand scientific concepts and how to use computational tools. %% cite notebook examples
%%- started development on UFF repo for foyer.
%%This is an example of how to create a version controlled forcefield which can be automatically applied to a compound.
%%<atom typing is a pain and doing it manually is bad cite foyer paper>
As for work towards my proposed plan, I have created a minimum working example of a coarse-graining and backmapping package which uses SMARTS strings to specify the bead chemistries. %%cite grits
This package will need further testing as it is tested on different compounds, but the proof of concept exists.
